Simulation Study: Varying Null Proportion (lower signal)

### 2018-06-08 datasets/simulations/simulations-varyinginformativeness-lowsignal.Rmd
Fix typo in 100% informative sims; add lower signal sims

## intermediary files we create below
info00_file <- file.path(resdir, "varyinginfo-benchmark-level00.rds")
info20_file <- file.path(resdir, "varyinginfo-benchmark-level20.rds")
info40_file <- file.path(resdir, "varyinginfo-benchmark-level40.rds")
info60_file <- file.path(resdir, "varyinginfo-benchmark-level60.rds")
info80_file <- file.path(resdir, "varyinginfo-benchmark-level80.rds")
info100_file <- file.path(resdir, "varyinginfo-benchmark-level100.rds")

@@

```{r parameters-shared}
m <- 20000                        # integer: number of hypothesis tests
tstat <- rnorm_generator(4)       # functional: dist of alternative test stats
tstat_dist <- rnorm_perturber(1)  # functional: sampling dist/noise for test stats
null_dist <- rnorm_2pvaluer(1)    # functional: dist to calc p-values
icovariate <- runif               # functional: independent covariate
```

@@

```{r info100-parameters}
pi0 <- pi0_varyinfo80(0.100)             # numeric: proportion of null hypotheses
seed <- 808
```

>>>>

## intermediary files we create below
info00_file <- file.path(resdir, "varyinginfo-lowsignal-benchmark-level00.rds")
info20_file <- file.path(resdir, "varyinginfo-lowsignal-benchmark-level20.rds")
info40_file <- file.path(resdir, "varyinginfo-lowsignal-benchmark-level40.rds")
info60_file <- file.path(resdir, "varyinginfo-lowsignal-benchmark-level60.rds")
info80_file <- file.path(resdir, "varyinginfo-lowsignal-benchmark-level80.rds")
info100_file <- file.path(resdir, "varyinginfo-lowsignal-benchmark-level100.rds")

@@

```{r parameters-shared}
m <- 20000                        # integer: number of hypothesis tests
tstat <- rnorm_generator(2)       # functional: dist of alternative test stats
tstat_dist <- rnorm_perturber(1)  # functional: sampling dist/noise for test stats
null_dist <- rnorm_2pvaluer(1)    # functional: dist to calc p-values
icovariate <- runif               # functional: independent covariate
```

@@

```{r info100-parameters}
pi0 <- pi0_varyinfo80(1.00)             # numeric: proportion of null hypotheses
seed <- 808
```

### 2018-06-08 datasets/simulations/simulations-varyingpi0-lowsignal.Rmd
Fix typo in 100% informative sims; add lower signal sims

---
title: "Simulation Study: Varying Null Proportion"
author: "Patrick Kimes"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: 
   html_document:
        toc: true
        toc_float: true
        highlight: tango
        number_sections: true
---

@@

## intermediary files we create below
null05_file <- file.path(resdir, "varyingpi0-benchmark-nullprop05.rds")
null10_file <- file.path(resdir, "varyingpi0-benchmark-nullprop10.rds")
null20_file <- file.path(resdir, "varyingpi0-benchmark-nullprop20.rds")
null50_file <- file.path(resdir, "varyingpi0-benchmark-nullprop50.rds")
null80_file <- file.path(resdir, "varyingpi0-benchmark-nullprop80.rds")
null90_file <- file.path(resdir, "varyingpi0-benchmark-nullprop90.rds")
null95_file <- file.path(resdir, "varyingpi0-benchmark-nullprop95.rds")
null99_file <- file.path(resdir, "varyingpi0-benchmark-nullprop99.rds")

>>>>

---
title: "Simulation Study: Varying Null Proportion (lower signal)"
author: "Patrick Kimes"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: 
   html_document:
        toc: true
        toc_float: true
        highlight: tango
        number_sections: true
---

@@

## intermediary files we create below
null05_file <- file.path(resdir, "varyingpi0-lowsignal-benchmark-nullprop05.rds")
null10_file <- file.path(resdir, "varyingpi0-lowsignal-benchmark-nullprop10.rds")
null20_file <- file.path(resdir, "varyingpi0-lowsignal-benchmark-nullprop20.rds")
null50_file <- file.path(resdir, "varyingpi0-lowsignal-benchmark-nullprop50.rds")
null80_file <- file.path(resdir, "varyingpi0-lowsignal-benchmark-nullprop80.rds")
null90_file <- file.path(resdir, "varyingpi0-lowsignal-benchmark-nullprop90.rds")
null95_file <- file.path(resdir, "varyingpi0-lowsignal-benchmark-nullprop95.rds")
null99_file <- file.path(resdir, "varyingpi0-lowsignal-benchmark-nullprop99.rds")
